\subsection{Week 1 (04 November 2024)}
Objective: Setup Frontend UI (visuals only), Develop Smart Contracts \\
Tasks: 
\begin{enumerate}
    \item Vikram: Implement frontend UI for Issuing Body to create credentials as smart contracts with configurable parameters (i.e. values passed to the smart contract constructor) and view a list of owned smart contracts and lists of associated credentials. Each credential in the credential list should display relevant metadata and provide an option for revocation given a reason. Frontend can fetch a list of pending verification requests and provide users with the option to approve or deny the request via cryptographic signature.
    \item Frederico: Implement frontend UI for Credential Holder to display a list of credentials owned and be able to approve/reject pending verification requests. Each credential should include metadata such as holder name, credential name, issuer name, issuer domain name, etc.
    \item Avni: Implement frontend UI for Verifier to submit verification requests to ResilientDB given contract address and credential ID, and view statuses of past requests.
    \item Ethan: Modify contract service and GraphQL service as necessary such that it supports generating
    address and private keys, along with verifying address ownership before deploying contract or executing contract functions.
    \item Zhenkai: Design and implement a smart contract that defines functions for issuing contracts. The contract needs to provide a constructor that allows for customization for an Issuing Body, such as credential name, expiration (if any), and other metadata.
\end{enumerate}
Associated Risks:
\begin{enumerate}
    \item Solidity Learning Curve: Figuring out the baseline smart contract system, and how to construct it to maximize security and minimize risk
    \item Frontend Learning Curve: Team members are not very familiar with frontend development frameworks, and learning a frontend framework may take time.
\end{enumerate}

