\subsection{Week 2 (11 November 2024)}
Objective: Implement frontend logic, integrating with Smart Contracts GraphQL service \\
Tasks: 
\begin{enumerate}
    \item Vikram: Integrate smart contract deployment with GraphQL service, utilizing the developed smart contract from Zhenkai. All Issuing Body rely on the same contract, only passing in different values to the contract constructor depending on the Issuing Body’s needs. An Issuing Body can technically intercept and modify the contract being deployed, but at their own risk. Addresses of smart contracts must be stored in the browser's local storage.
    \item Frederico: Implement credential import feature that stores passphrase-protected credentials to storage. To verify whether the credential is valid, use GraphQL to confirm that the credential is stored on the correlated smart contract.
    \item Avni: Integrate Verifier UI with GraphQL service. The frontend must periodically poll the GraphQL service for the status of pending verification requests.
    \item Ethan: Test smart contract creation and credential issuance with ResContract CLI.
        Continue to explore and submit bug fixes and patches necessary to the ResContract and
        ResilientDB source code to improve ResilientDB and the corresponding services and projects.
    \item Zhenkai: Set up GraphQL Smart Contract service on the team-wide shared VM and implement
        account creation and key storage on the frontend by integrating with GraphQL service. 
        Collaborate with Ethan to implement and modify the ResilientDB GraphQL endpoints and ResilientDB contract service.
    \item All: Prepare the midterm progress report.
\end{enumerate}
Associated Risks:
\begin{enumerate}
    \item Unfamiliarity with ResilientDB Codebase: As we dig deeper into ResilientDB codebase to develop required functionalities for ResCred, a comprehensive understanding of contract service, contract CLI, and the wrapper GraphQL endpoints are required. Such an understanding may take more time to develop than expected. 
\end{enumerate}

